Novelty Detection Using Graphical Models for Semantic Room Classification

### 2011-05-17 semantic-nd/article.tex
Pronobis introduction in scene categorization and using visual and laser scans to classification

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}
% TODO(pronobis): general comment about many .... approches to place categorization.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}
% TODO(pronobis): general comment about many .... approches to place categorization.
The problem of room categorization based on visual information was first addressed
in the computer vision community. In this case, the research focused mainly on the
problem of classifying single images captured in indoor or outdoor environments
(scene classification). At the same time, robotics researchers initially employed
the 2D laser range sensor being much more robust to variations occurring in the
environment and much easier to handle computationally in real time.
